A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-03-09 ISMB/ResponseToReviewers-Incarnation-ISMB-2013.tex

\Comment{Since you have shown that RNAinverse biases the GC-content to 50-70, the GC-content increase/decrease for lower/higher IncaRNAtion values, resp., when successivly applying RNAinverse (Supp 5.2) is to be expected.}
\Answer{Absolutely. However, the point of this section was not to insist on this issue, but rather to show that our glocal approach, starting with a global sampling followed by a postprocessing of unpaired regions using \RNAinverse, does not {\em drift} too much towards regions of high \GCContent{}s. We rephrased the text of this section to make this conclusion appear more clearly, and changed the layout of Table 2 to make the shift in \GC more explicit.}

\Comment{Is there a way to apply sequence constraints within IncaRNAtion? This is something most end user will want.
}
\Answer{We added this feature to our implementation, which now accepts a constraint mask consisting in a sequence of IUPAC symbols (e.g. 'N' for unconstrained position, or G for Guanine-only\ldots). We also briefly mention this feature in the definition of our probabilistic model.}

\Comment{What is the time consumption/complexity of the GC-weight parameter $x_{gc}$ identification within Sec. 2.2.3? And are these values length-/structure-independent or do they have to be computed for each structure individually?}
\Answer{These values are structure/\GCContent-dependent, and must be recomputed for any new input. We made this point clearer in the description of the adaptive sampling procedure, and the influence on the complexity of the number $M$ of iterations. Typically, 4 or 5 iterations are required to get a good approximation of the best value $x_{gc}$, and our binary search approach provably offers a linear convergence (in term of the number of correct decimals) towards the closest representable value of $x_{gc}$.}

@@

\Comment{3-4) Typos\ldots}
\Answer{We fixed those typos.}

\subsection{Reviewer \#3}

\Comment{(1) There are many points where you iterate over "all sequences of length $|S|$" or all of those which can fold into $S$; it is not always clear. Why not introduce $F(s)$ for the folding space of a sequence, and $F^{-1}(S)$ for the inverse folding space of a structure, and simply use $F^{-1}(S)$ where this is what you mean?}
\Answer{While we agree that this proposition would lead to compact and well-defined mathematical statements, we prefer a implicit definition of the compatibility of a sequence to a given structure. Namely, we always allow every possible sequence of a length $|S|$ to be a member of the inverse folding space, possibly assigning some  energy penalty to it  (typically $+\infty$, or $\beta$) when some constraints are violated (restriction on allowed base-pairs, position-specific constraints...). The inverse folding space is therefore implicitly defined as the set of sequences having finite energy, and our algorithm is arguably more prone to generalization, e.g. to capture non-canonical base-pairs which are increasingly considered by the field of RNA bioinformatics.
}

\Comment{(2) You make the computation of $Z$ look like yet another set of DP recurrences, and as a consequence, you need a proof to show that it is linear in $n$. Surely, the reader wonders at that point how you can iterate over $(i,j)$ and compute an $(n,n)$ table in less than quadratic time. This mis-led understanding is created by the Nussinovic style of the recurrences.
 What you actually compute is a sparse, tree-shaped segment of that $(i,j)$-table.
 Why not represent the given structure as a tree of Empty, Singleton, Pair and Bifurcation nodes, such as 
\begin{align*}
  S<\texttt{.},B<P<\texttt{(},S<\texttt{.},E>,\texttt{)},P<\texttt{(},Em,\texttt{)}>>> \text{ for {\tt .(.)()}}  ? 
\end{align*}
 (You do not even need to explicitly represent the dots and brackets at the leaves.)\\
 Then, computation of $Z$ becomes just structural recursion on the tree,
     $Z(a,b, t) =$ defined by case analysis on t, such that, for example,
     $Z(a,b,P<'(',r,')'>)$ calls on $Z(a',b' r)$ for all $a'$ and $b'$.
And the result of the computation is just the tree annotated with the $Z_{ab}$ values. 
This way it is more transparent what is going on, and it is obvious that space and time are linear in $n$, because the size of the tree is in $O(n)$.}
\Answer{Great suggestion. However, adopting a pure tree-like representation would require elaborating on the correspondence between trees and structures, and might lead to technicalities in the context of stacking base-pairs. Therefore, we completely rewrote our equations, figure and algorithm to adopt a classic dot-parenthesis representation. While the end result may be less elegant than expected with a tree-like presentation, this rewrite has the merit of dropping the double subscripts, hopefully better conveying the  intuition underlying the complexity claim in our original manuscript.}

### 2013-03-10 ISMB/ResponseToReviewers-Incarnation-ISMB-2013.tex

First of all, the authors wish to express their gratitude to the reviewers for their encouraging comments and constructive criticisms, which we tried to address in this revised version of our manuscript.

\section{Detailed responses}

\subsection{Reviewer \#1}

\Comment{The benchmark only compares to RNAinverse which is outperformed by most methods you name in your introduction. Thus, a real benchmarking would have to compare to other methods as well. For most, source code packages are available.}
\Answer{In addition to \RNAinverse~\cite{Hofacker:1994}, we systematically benchmarked \ourprog against an extended selection of available tools, including \NUPACK~\cite{Zadeh:2011fk}, \frankenstein~\cite{Lyngso:2012vn}, \RNASSD~\cite{Aguirre-Hernandez:2007kx}, \INFORNA~\cite{Busch:2006uq} and \RNAexinv~\cite{Avihoo:2011fk}. While the page limitations associated with a conference submission do not allow for a an exhaustive discussion, we now report in the revised manuscript some of the most striking results. Mainly, with the exception of \RNASSD, none of the latest version of our competitor allows an explicit control over the \GCContent, resulting in designs that are usually highly concentrated in \GCContent (with means ranging from 50\% to 80\% depending on the software). \textbf{FIXME: What should I add here? I think Vlad already added the histogram for the distribution of GC already (?)}
}

@@

\Comment{Since you have shown that RNAinverse biases the GC-content to 50-70, the GC-content increase/decrease for lower/higher IncaRNAtion values, resp., when successivly applying RNAinverse (Supp 5.2) is to be expected.}
\Answer{Absolutely. However, the point of this section was not to insist on this issue, but rather to show that our glocal approach, starting with a global sampling followed by a postprocessing of unpaired regions using \RNAinverse, does not {\em drift} too much towards regions of high \GCContent{}s. We rephrased the text of this section to make this conclusion appear more clearly, and changed the layout of Table 2 to make the shift in \GC more explicit.}

\Comment{Is there a way to apply sequence constraints within IncaRNAtion? This is something most end user will want.
}
\Answer{We added this feature to our implementation, which now accepts a constraint mask consisting in a sequence of IUPAC symbols (e.g. 'N' for unconstrained position, or G for Guanine-only\ldots). We also briefly mention this feature in the definition of our probabilistic model.}

\Comment{What is the time consumption/complexity of the GC-weight parameter $x_{gc}$ identification within Sec. 2.2.3? And are these values length-/structure-independent or do they have to be computed for each structure individually?}
\Answer{These values are structure/\GCContent-dependent, and must be recomputed for any new input. We made this point clearer in the description of the adaptive sampling procedure, and the influence on the complexity of the number $M$ of iterations. Typically, 4 or 5 iterations are required to get a good approximation of the best value $x_{gc}$, and our binary search approach provably offers a linear convergence (in term of the number of correct decimals) towards the closest representable value of $x_{gc}$.}

\Comment{Is the method available?}
\Answer{\textbf{FIXME: Do you prefer a redirection to the git-hub repo or should we setup a basic web server?}}

@@

\subsection{Reviewer \#2}

\Comment{1) The $x^{\gc(s)}$ in equation (1) seems to me a novel contributing term that is of high importance. Perhaps its introduction should be highlighted more in the text.}
\Answer{We tried to make this point clearer in our revised version. However, it should be noted that this contribution is not a goal in itself, but rather a mean to perform stochastic sampling with respect to the weighted distribution. This distribution has all sorts of desirable mathematical properties, among which the fact that induced distributions for additive features (here the \GCContent) are nicely concentrated, allowing for a rejection-based approach.
\textbf{FIXME: Should we really says it's not a goal. This seems to diminish our work... I'll try to find a way to re-formulate that. I agree with the content though.}
}

\Comment{2) Concerning Table 2 in the Supplementary data, the way it is written (IncaRNAtion + RNAinverse) it looks like "glocal" search heuristic whereas in the table it seems local. Perhaps there is a small typo ambiguity that can be resolved.}
\Answer{Reviewer \#1 also pointed out some inconsistency/unclarity in our previous formulation. The second column indeed showed the final \GCContent of the glocal approach, following the postprocessing of sequences with a local-search approach. While such a postprocessing tends to reestablish \GCContent{}s that are  closer to 50\% \GC, this shift remains reasonable (at most ~6\% \GC). Furthermore, this shift is very predictable and offers the user the possibility to \emph{overshoot} for a more extreme \GCContent with the global approach, knowing that the postprocessing step will tend to average it.
\textbf{FIXME: We could eventually emphasize that we bring \RNAinverse in a region which is likely to statisfy the  MFE criterion and thus will require only minimal adjustments.}}

@@

\Comment{3-4) Typos\ldots}
\Answer{We fixed those typos.}

\subsection{Reviewer \#3}

\Comment{(1) There are many points where you iterate over "all sequences of length $|S|$" or all of those which can fold into $S$; it is not always clear. Why not introduce $F(s)$ for the folding space of a sequence, and $F^{-1}(S)$ for the inverse folding space of a structure, and simply use $F^{-1}(S)$ where this is what you mean?}
\Answer{While we agree that this proposition would lead to compact and well-defined mathematical statements, we prefer a implicit definition of the compatibility of a sequence to a given structure. Namely, we always allow every possible sequence of a length $|S|$ to be a member of the inverse folding space, possibly assigning some  energy penalty to it  (typically $+\infty$, or $\beta$) when some constraints are violated (restriction on allowed base-pairs, position-specific constraints...). The inverse folding space is therefore implicitly defined as the set of sequences having finite energy, and our algorithm is arguably more prone to generalization, e.g. to capture non-canonical base-pairs which are increasingly considered by the field of RNA bioinformatics.
\textbf{FIXME: Wow... that's the first time I see you refusing to be more formal :) }
}

@@

\Comment{(3) Figure 1 is also a bit misleading. Make it clear that the stochastic choice is NOT made over the three cases depicted. The case is always fixed for given $i$, just the bases are chosen.}
\Answer{Absolutely. We changed this figure, which now explicitly distinguishes between the three different cases (different left-hand side diagrams), and also features the base emission probabilities.}

\Comment{(4) Section 2.2.3 is titled "Rejecting unsuitable candidates". It explains that candidates tend to be quite suitable, but somewhere, you should actually tell who is rejected and when ... }
\Answer{We completely rewrote this section, which now starts by explicitly reminding the problem addressed by the algorithm.}

\Comment{(5) recurring: "free-nucleotides in loops" -- isn't that the same, being "free" and in a loop? And: drop the hyphen.}
\Answer{The term of loop is sometimes used in a broader sense, which could be informally summarized as "a closed cyclic sequence of bases, connected either by the backbone or by base-pairs" (such that each connection but one goes in the $5'\to3'$ direction). This alternate definition was already used in the earlier works of M. Zuker, and maybe goes further back in the prehistory of RNA bioinformatics. Under this definition,  some of the bases involved in a loop may be paired, therefore we use the adjective to lift any ambiguity.
\textbf{FIXME: Alternatively we could use the term of ``unpaired nucleotides''?}
}

### 2013-03-10 ISMB/main_ISMB.tex
Typos + Changed sampling figure
method over (except typos)
Typos
bioinfo template

\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in,right=1in,left=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{tcolorbox}
\usepackage{relsize}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos]{todonotes}

@@

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{relsize}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{decorations}
\usetikzlibrary{snakes}
\pgfdeclarelayer{background}
\pgfdeclarelayer{backbackground}
\pgfdeclarelayer{foreground}
\pgfsetlayers{backbackground,background,main,foreground}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newcommand{\ourprog}{\texttt{IncaRNAtion}\xspace}

@@

\newcommand{\RNAmutants}{\texttt{RNAmutants}\xspace}
\newcommand{\RNApyro}{\texttt{RNApyro}\xspace}
\newcommand{\RNAinverse}{\texttt{RNAinverse}\xspace}
\newcommand{\RNASSD}{\texttt{RNA-SSD}\xspace}
\newcommand{\INFORNA}{\texttt{INFO-RNA}\xspace}
\newcommand{\NUPACK}{\texttt{NUPACK}\xspace}
\newcommand{\RNAiFOLD}{\texttt{RNAiFOLD}\xspace}
\newcommand{\frankenstein}{\texttt{Frnakenstein}\xspace}
\newcommand{\RNAexinv}{\texttt{RNAexinv}\xspace}
\newcommand{\rnaDesign}{\texttt{rnaDesign}\xspace}
\newcommand{\RNAensign}{\texttt{RNA-ensign}\xspace}
\newcommand{\GCContent}{\Gb\Cb-content\xspace}
\newcommand{\SFold}{\texttt{SFold}\xspace}

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\farna}{\texttt{FARNA}\xspace}
\newcommand{\mcfoldmcsym}{\texttt{MC-Pipeline}\xspace}
\newcommand{\mcfold}{\texttt{MC-Fold}\xspace}
\newcommand{\mcsym}{\texttt{MC-Sym}\xspace}
\newcommand{\nast}{\texttt{NAST}\xspace}
\newcommand{\ifoldrna}{\texttt{iFoldRNA}\xspace}
\newcommand{\rnafold}{\texttt{RNAfold}\xspace}
\newcommand{\rnasubopt}{\texttt{RNAsubopt}\xspace}
\newcommand{\rnawolf}{\texttt{RNAwolf}\xspace}
\newcommand{\rnastructure}{\texttt{RNAstructure}\xspace}
\newcommand{\contrafold}{\texttt{contrafold}\xspace}
\newcommand{\unafold}{\texttt{unafold}\xspace}
\newcommand{\rnadd}{\texttt{RNA2D3D}\xspace}
\newcommand{\assemble}{\texttt{assemble}\xspace}
\newcommand{\fred}{\texttt{FR3D}\xspace}
\newcommand{\rnajunction}{\texttt{RNAjunction}\xspace}
\newcommand{\rnamotif}{\texttt{RNAmotif}\xspace}
\newcommand{\treefolder}{\texttt{TreeFolder}\xspace}
\newcommand{\barnacle}{\texttt{BARNACLE}\xspace}
\newcommand{\contextfold}{\texttt{contextfold}\xspace}

\newcommand{\RNASTRAND}{{\sf RNA STRAND}\xspace}

%\newcommand{\citep}{\cite}
\newcommand{\Z}[2]{\mathcal{Z}{\substack{(#1)\\ [#2]}}}
\newcommand{\Y}[3]{\mathcal{Y}_{\substack{(#1)\\ [#3]}}^{#2}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Kron}{\delta}
\newcommand{\ub}{\bullet}

\newcommand{\Ab}{{\sf{A}}\xspace}
\newcommand{\Cb}{{\sf{C}}\xspace}
\newcommand{\Gb}{{\sf{G}}\xspace}
\newcommand{\Ub}{{\sf{U}}\xspace}

\newcommand{\gc}{{\#\text{{\sf gc}}}}
\newcommand{\PE}[1]{E(#1)}
\newcommand{\EI}{\text{EI}}
\newcommand{\ES}{\text{{\sf Es}}}
\newcommand{\ISO}{\text{ISO}}
\newcommand{\Prob}{\text{P}}
\newcommand{\Target}{\text{\sf S}}
\newcommand{\CNBP}[1]{\gamma(#1)}

\newcommand{\CFramed}[2][gray]{\begin{tcolorbox}[colframe=#1,title=To be included only if space allows\ldots,colback=white]#1\end{tcolorbox}}
\renewcommand{\CFramed}[2][gray]{}

\title{A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution}
\author{Vladimir Reinharz$^1$, Yann Ponty$^{2,*}$, J\'er\^{o}me Waldisp\"{u}hl$^{1,*}$}
\date{$^1$ School of Computer Science, McGill University, Montreal, Canada, $^2$ Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.\\ \small $^*$Corresponding authors: \texttt{jeromew@cs.mcgill.ca}, \texttt{yann.ponty@lix.polytechnique.fr}}

%Last thing before BEGIN DOC for links to appear in pdf

%  \usepackage{hyperref}
%  \hypersetup{colorlinks}
%              citecolor=black,
%              filecolor=black%
%              linkcolor=black%
%              urlcolor=black%
%              pdftex}

\begin{document}
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
\noindent
\textbf{Motivations:} The design of RNA sequences folding into predefined secondary structures is a milestone for many synthetic biology and gene therapy studies. Most of the current software uses similar local search strategies (i.e. a random seed is progressively adapted to acquire the desired folding propertues) and more importantly do not allow the user to control explicitly the nucleotide distribution such as the \GCContent in their sequences. However, the latter is an important criterion for large-scale applications as it could presumably be used to design sequences with better transcription rates and/or structural plasticity.\\
\noindent
\textbf{Results:}
In this paper, we introduce \ourprog, a novel algorithm to design RNA sequences folding into target secondary structures with a predefined nucleotide distribution.  \ourprog uses a global sampling approach and weighted sampling techniques. We show that our approach is fast (i.e. running time comparable or better than local search methods), seed-less (we remove the bias of the seed in local search heuristics), and successfully generates high-quality sequences (i.e. thermodynamically stable) for any \GCContent. To complete this study, we develop an hybrid method combining our global sampling approach with local search strategies. Remarkably, our glocal methodology overcomes both local and global approaches  for sampling sequences with a specific GC content and target structure.\\
\noindent
\textbf{Key words:} RNA, secondary structure, design, weighted sampling, GC-content.
\end{abstract}

@@

\bibliographystyle{plainnat}
\bibliography{RNApyro}

>>>>

\documentclass{bioinfo}
\copyrightyear{2013}
\pubyear{2013}
%\usepackage[top=1in, bottom=1in,right=1in,left=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{tcolorbox}
\usepackage{relsize}
\usepackage{natbib}
\usepackage[colorinlistoftodos]{todonotes}

@@

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{cleveref}
\usepackage{url}

\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{decorations}
\usetikzlibrary{snakes}
\pgfdeclarelayer{background}
\pgfdeclarelayer{backbackground}
\pgfdeclarelayer{foreground}
\pgfsetlayers{backbackground,background,main,foreground}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{description}{Description}

\crefmultiformat{equation}{Equations~(#2#1#3)}%
{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}

@@

\input{macros}

\begin{document}
\firstpage{1}

\title{A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution}
\author{Vladimir Reinharz$^1$, Yann Ponty$^{2,*}$, J\'er\^{o}me Waldisp\"{u}hl$^{1,*}$\footnote{to whom correspondence should be addressed}}
\address{$^1$ School of Computer Science, McGill University, Montreal, Canada\\ $^2$ Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\maketitle
%\section{}
%\subsection{}
\begin{abstract}
\section{Motivations:} The design of RNA sequences folding into predefined secondary structures is a milestone for many synthetic biology and gene therapy studies. Most of the current software uses similar local search strategies (i.e. a random seed is progressively adapted to acquire the desired folding propertues) and more importantly do not allow the user to control explicitly the nucleotide distribution such as the \GCContent in their sequences. However, the latter is an important criterion for large-scale applications as it could presumably be used to design sequences with better transcription rates and/or structural plasticity.

\section{Results:}
In this paper, we introduce \ourprog, a novel algorithm to design RNA sequences folding into target secondary structures with a predefined nucleotide distribution.  \ourprog uses a global sampling approach and weighted sampling techniques. We show that our approach is fast (i.e. running time comparable or better than local search methods), seed-less (we remove the bias of the seed in local search heuristics), and successfully generates high-quality sequences (i.e. thermodynamically stable) for any \GCContent. To complete this study, we develop an hybrid method combining our global sampling approach with local search strategies. Remarkably, our glocal methodology overcomes both local and global approaches  for sampling sequences with a specific GC content and target structure.
\section{Availability:} 
Our method is freely available at WEBSITE INCARNATION
\section{Contact:} \href{jeromew@cs.mcgill.ca}{jeromew@cs.mcgill.ca}, \href{yann.ponty@lix.polytechnique.fr}{yann.ponty@lix.polytechnique.fr}\\
\noindent
\textbf{Key words:} RNA, secondary structure, design, weighted sampling, GC-content.
\end{abstract}

@@

\bibliographystyle{natbib}
\bibliography{RNApyro}

### 2013-03-10 ISMB/results_ISMB.tex
Typos
bioinfo template

\subsection{Implementation}
\label{sec:implementation}
Our software, \ourprog, was implemented in {\tt Python~2.7}. We used
\RNAinverse from the \textit{Vienna Package 2.0}~\cite{Hofacker:1994}.
All time benchmarks were run on a single AMD Opteron(tm) 6278 Processor  at 2.4 GHz with cache of 512 KB.
The penalty $\beta$, associated with invalid base-pairs, was set to $15$.

\begin{figure}[t!]
	\centering
	\includegraphics[width=\textwidth]{Figures/time_rnastrand_clustered_rnainverse_100samples_fix}
	\caption{Average time in seconds to generate one sequence. We explicitly show 
	the time spent by \ourprog (full line) and \texttt{RNAinverse} (dashed) for various \GCContent. The first plot is in function
	of the length of the structures. The second is in function of the stack
	density (i.e. $2\cdot\#stacks/length$) and the latter in function of 
	the proportion of free nucleotides (i.e. unpaired bases) within loops.}
	\label{fig:time}	
\end{figure}

@@

 \begin{figure}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{Figures/bins_distribution.png}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure}

@@

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{Figures/mfe_struct_solve_nornainverse.png}
	\caption{Quality of \ourprog results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure}

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{Figures/mfe_struct_solved}
	\caption{Quality of \texttt{Incarnation+RNAinverse} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[scale=0.45]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/nb_sols_entropy.png}
	\caption{Number of solutions generated and their average entropy. 
	The last row presents only the entropy of the nucleotides inside base 
	pairs.}
	\label{fig:nb_sols_entropy}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/freq.png}
	\caption{Average Boltzmann probability of the MFE.}
	\label{fig:freq}
\end{figure}

@@

\label{fig:rnainverse}

>>>>

\subsection{Implementation}
\label{sec:implementation}
Our software, \ourprog, is available at \oururl and was implemented in {\tt Python~2.7}. We used
\RNAinverse from the \textit{Vienna Package 2.0}~\cite{Hofacker:1994}.

All time benchmarks were run on a single AMD Opteron(tm) 6278 Processor  at 2.4 GHz with cache of 512 KB.
The penalty $\beta$, associated with invalid base-pairs, was set to $15$.

\begin{figure}[t!]
	\centering
 	\includegraphics[width=0.5\textwidth]{Figures/time_rnastrand_clustered_rnainverse_100samples_fix}
	\caption{Average time in seconds to generate one sequence. We explicitly show 
	the time spent by \ourprog (full line) and \texttt{RNAinverse} (dashed) for various \GCContent. The first plot is in function
	of the length of the structures. The second is in function of the stack
	density (i.e. $2\cdot\#stacks/length$) and the latter in function of 
	the proportion of free nucleotides (i.e. unpaired bases) within loops.}
	\label{fig:time}	
\end{figure}

@@

 \begin{figure}[ht!]
 	\centering
	\includegraphics[width=0.5\textwidth]{Figures/bins_distribution.png}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure}

@@

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=0.5\textwidth]{Figures/mfe_struct_solve_nornainverse.png}
	\caption{Quality of \ourprog results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure}

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=0.5\textwidth]{Figures/mfe_struct_solved}
	\caption{Quality of \texttt{Incarnation+RNAinverse} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[width=0.5\textwidth]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.5\textwidth]{Figures/nb_sols_entropy.png}
	\caption{Number of solutions generated and their average entropy. 
	The last row presents only the entropy of the nucleotides inside base 
	pairs.}
	\label{fig:nb_sols_entropy}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.5\textwidth]{Figures/freq.png}
	\caption{Average Boltzmann probability of the MFE.}
	\label{fig:freq}
\end{figure}

@@

%\label{fig:rnainverse}
